Evolution of ORM Systems: Formal Foundations

### 2012-12-20 doc/description.tex
updated addAsociation so it handles data too

\begin{document}
\tableofcontents

\newpage
\section{ORM System}
The ORM system represents an application created using object oriented language and relational database. The components of such an application and theirs relations are in Figure \ref{fig:appStructure}. We define the application in our model as:

@@

\subsubsection{Add Association}
$
\Phi_{AddAssociation}(a, d) = \begin{cases}
\inference{ \exists t_s, t_t \in tables(d) : name(t_s) = name(owningClass(a)) \\ \wedge name(t_t) = reference(a) \\ \wedge \not \exists f \in foreignKeys(t_t) : name(f) = name(a) }{ \rho(a,d) }
 \end{cases}
$

@@

\subsubsection{Altering of a System}

>>>>

\title{Evolution of ORM Systems: Formal Foundations}
\author{Ondrej Macek}

\begin{document}
\tableofcontents \newpage

\maketitle
\section{ORM System}
The ORM system represents an application created using object oriented language and relational database. The components of such an application and theirs relations are in Figure \ref{fig:appStructure}. We define the application in our model as:

@@

\subsubsection{Add Association}
$
\Phi_{AddAssociation}(a, f_m, d) = \begin{cases}
\inference{ \exists t_s, t_t \in tables(d) : name(t_s) = name(owningClass(a)) \\ \wedge name(t_t) = reference(a) \\ \wedge \not \exists f \in foreignKeys(t_t) : name(f) = name(a) \\ startCardinality(a) \leq 1}{\begin{gathered}
\rho(a,d) \wedge \forall r \in f_m(owningClass(a), reference(a)) : \\ data(t_t) \cup row(name(t_s), pair(name(a), \\ value(primaryKey(first(r)))) 
\end{gathered}
 }
 \\ \\
\inference{ \exists t_s, t_t \in tables(d) : name(t_s) = name(owningClass(a)) \\ \wedge name(t_t) = reference(a) \\ \wedge \not \exists f \in foreignKeys(t_t) : name(f) = name(a) \\ startCardinality(a) > 1}{\begin{gathered}
\rho(a,d) \wedge \forall r \in f_m(owningClass(a), reference(a)),\\ t \in tables(d) : name(t) = name(a) : \\ data(t) \cup row(name(a), pair(name(t_s), \\ value(primaryKey(first(r)))) pair(name(t_t), \\ value(primaryKey(second(r)))))
\end{gathered}
 }

@@

\subsubsection{Altering a System}
